Measurement of deeply virtual Compton scattering off Helium-4 with CLAS at Jefferson Lab

### 2021-02-02 eg6-letters/long-paper/prc-dvcshelium.tex
Update figures and author list

\documentclass{article}
\usepackage[left=3.5cm,right=2.5cm,top=2cm,bottom=2cm,includefoot,includehead,headheight=15pt]{geometry}
%\usepackage{lineno}
%\documentclass[aps,prc,preprint,superscriptaddress]{revtex4}
%\usepackage{amsmath,amssymb}             % AMS Math
%\usepackage[francais]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern,textcomp}
\usepackage{setspace}
\usepackage{microtype}
\usepackage{epigraph}
\usepackage{natbib}
%\usepackage[scaled]{helvet}
%\usepackage[pagebackref,hyperindex=true]{hyperref}
%\usepackage{pdfpages}
\usepackage{graphicx}
\usepackage{array}
\usepackage{amsmath} 
\usepackage{multirow}

@@

%\input author_list.tex

\date{\today}
%TODO
\maketitle

@@

%\maketitle

@@

\begin{figure}[tbp]
\center
\includegraphics[width=16cm]{fig3/Coherent_ALU_phi_90.pdf}
\caption{The BSA at 90° as a function of $Q^2$ (top panel), $x$ (middle panel) and $-t$ (lower panel).
	Our results are shown with black squares, HERMES results 
	with green circles~\cite{Airapetian:2009cga}. Theoretical predictions 
	by Liuti \textit{et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} are shown 
	by the red full line and the dashed blue line, while the calculation by Fucini 
	\textit{et al.}~\cite{Fucini:2018gso} is shown with the magenta long dashed line.}
\label{fig:CohALU90}
\end{figure}

@@

\begin{figure}[tbp!]
\center
\includegraphics[width=7.4cm]{fig3/ALU_90_p_vs_Q2_shortscenrario.pdf}
\includegraphics[width=7.4cm]{fig3/ALU_90_p_vs_t_shortscenrario.pdf}
\includegraphics[width=7.4cm]{fig3/ALU_90_p_vs_x_shortscenrario.pdf}
	\caption{The BSA at 90° as a function of  $Q^2$ (top left), $x$ (top right) and 
	$-t$ (bottom). Our measurement is represented with black squares and the HERMES 
	measurement \cite{Airapetian:2009cga} with green circles. Theoretical predictions 
	by Liuti {\it et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} are shown 
	by the red full line and the dashed blue line, while the calculation by Fucini 
	{\it et al.}~\cite{Fucini:2019xlc} is shown with the magenta long dashed line.}
\label{fig:IncALU}
\end{figure}

\begin{figure}[tbp!]
\center
\includegraphics[width=7.4cm]{fig3/ALU_ratioInc_Q2_shortscenrario.pdf}
\includegraphics[width=7.4cm]{fig3/ALU_ratioInc_t_shortscenrario.pdf}
\includegraphics[width=7.4cm]{fig3/ALU_ratioInc_x_shortscenrario.pdf}
	\caption{DVCS BSA ratio of the bound proton to the free proton as a function of 
	$Q^2$ (top left), $x$ (top right) and $-t$ (bottom). The present measurement is 
	represented with black squares and the HERMES 
	measurement \cite{Airapetian:2009cga} with green circles. Theoretical predictions 
	by Liuti {\it et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} are shown 
	by the red full line and the dashed blue line, a calculation adapted by Fucini 
	{\it et al.}~\cite{Fucini:2019xlc} is shown with the magenta long dashed line and 
	the black dot-dashed line is the calculation by Guzey {\it et al.}~\cite{Guzey:2008th}.}
\label{fig:IncRatios}
\end{figure}

>>>>

%\documentclass{article}
%\usepackage[left=3.5cm,right=2.5cm,top=2cm,bottom=2cm,includefoot,includehead,headheight=15pt]{geometry}
%\usepackage{lineno}
\documentclass[aps,prc,preprint,superscriptaddress]{revtex4}
%\usepackage{amsmath,amssymb}             % AMS Math
%\usepackage[francais]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern,textcomp}
\usepackage{setspace}
\usepackage{microtype}
\usepackage{epigraph}
\usepackage{natbib}
%\usepackage[scaled]{helvet}
%\usepackage[pagebackref,hyperindex=true]{hyperref}
%\usepackage{pdfpages}
\usepackage{graphicx}
\usepackage{array}
\usepackage{amsmath} 
\usepackage{multirow}

@@

\input author_list.tex

\date{\today}

@@

\maketitle

@@

\begin{figure}[tbp]
\center
\includegraphics[width=16cm]{fig3/Coherent_ALU_phi_90.pdf}
\caption{The BSA at 90° as a function of $Q^2$ (top panel), $x$ (middle panel) and $-t$ (lower panel).
	Our results are shown with black squares, HERMES results 
	with green circles~\cite{Airapetian:2009cga}. The theoretical prediction 
	by Liuti \textit{et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} is shown 
	by the full blue line, while the calculation by Fucini 
	\textit{et al.}~\cite{Fucini:2018gso} is shown with the magenta dashed line.}
\label{fig:CohALU90}
\end{figure}

@@

\begin{figure}[tbp!]
\center
\includegraphics[width=7.4cm]{fig3/ALU_90_p_vs_Q2_shortscenrario.pdf}
\includegraphics[width=7.4cm]{fig3/ALU_90_p_vs_t_shortscenrario.pdf}
\includegraphics[width=7.4cm]{fig3/ALU_90_p_vs_x_shortscenrario.pdf}
	\caption{The BSA at 90° as a function of  $Q^2$ (top left), $x$ (top right) and 
	$-t$ (bottom). Our measurement is represented with black squares and the HERMES 
	measurement \cite{Airapetian:2009cga} with green circles. The theoretical prediction 
	by Liuti {\it et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} is shown 
	by the full blue line, while the calculation by Fucini 
	{\it et al.}~\cite{Fucini:2019xlc} is shown with the magenta dashed line.}
\label{fig:IncALU}
\end{figure}

\begin{figure}[tbp!]
\center
\includegraphics[width=7.4cm]{fig3/ALU_ratioInc_Q2_shortscenrario.pdf}
\includegraphics[width=7.4cm]{fig3/ALU_ratioInc_t_shortscenrario.pdf}
\includegraphics[width=7.4cm]{fig3/ALU_ratioInc_x_shortscenrario.pdf}
	\caption{DVCS BSA ratio of the bound proton to the free proton as a function of 
	$Q^2$ (top left), $x$ (top right) and $-t$ (bottom). The present measurement is 
	represented with black squares and the HERMES 
	measurement \cite{Airapetian:2009cga} with green circles. The theoretical prediction
	by Liuti {\it et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} is shown 
	by the full blue line, the calculation by Fucini 
	{\it et al.}~\cite{Fucini:2019xlc} is shown with the magenta dashed line, and 
	the black dot-dashed line is the calculation by Guzey {\it et al.}~\cite{Guzey:2008th}.}
\label{fig:IncRatios}
\end{figure}
